The effect of prenatal environment on brain metabolic function and perception in a lizard

### 2025-10-14 ms.qmd
Update ms.qmd

### Data accessibility  
All data, data description, and R code are available in public repository [https://github.com/Pablo-Recio/CORT-Temp_PreyD](https://github.com/Pablo-Recio/CORT_Temp_PreyD).

>>>>

### Data accessibility  
All data, data description, and R code are available in public repository [https://github.com/Pablo-Recio/CORT_Temp_PreyD](https://github.com/Pablo-Recio/CORT_Temp_PreyD).
